Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-09-07 scagnostics.Rmd
Motivation from physics?

>>>>

(Motivation - something along the lines of the following paragraph, but more understandable, maybe giving concrete example - e.g. dec vs time from neutron star posterior?)
One motivation to consider projection pursuit indices beyond the ones considered so far is coming from physics applications where a standard method is the determination of physcis parameters by means of global fits to large experimental datasets. Typically models will come with a handful of free parameters, model predictions will be calculated by means of numeric tools and the best fit parameters are evaluated by comparing predictions to a large number of observations. Fit results will encode relations between the model parameters dictaded by the available observations, for example if two parameters control predictions for a well constrained observable, looking at the distribution of parameter combinations which are a good fit will be instructive. A standard example is to study the likelihood or posterior distribution in pair-wise 2-d plots, where the selection of parameters if often guided by knowledge of the underlying physics. A major challenge is the progressing complexity in all three aspects: models with larger parameter spaces are being studied, computation of observable predictions is increasingly complex and the number of experimental observations relevant to a given model is growing. Methods for the detection of "interesting" views that can aid physics intuition are therefore more and more relevant.
